---
title: "My Website"
---

Hello, Website!

For more information about simple R Markdown websites, please read the documentation at https://bookdown.org/yihui/rmarkdown/rmarkdown-site.html.

Please also note that simple R Markdown sites are _not_ based on **blogdown**. They are probably good for websites with only a few Rmd documents. For larger-scale and more sophisticated websites (such as blogs), you may want to use **blogdown** instead: https://github.com/rstudio/blogdown.

# Loading A File
```{r}
library(neuralnet)
library(caret)
library(tidyverse)
```
#Checking The data from data frame
```{r}
head(diamonds)
```
```{r}
df<-diamonds %>%
    filter(cut %in% c("Ideal","Good"))
#head(df)
df<-sample_n(df,5000)
#dim(df)
df$binary<- ifelse(df$cut=="Ideal", 1,0)
head(df)

```
```{r}
df$binary<-as.factor(df$binary)
names(df)
df<-df[,-2]
head(df)
```
```{r}
rows<-createDataPartition(df$binary,p=.7, list = F, times = 1)
head(rows)
train<-df[rows,]
head(train)
test<-df[-rows,]
head(test)
```
```{r}
library(ranger)
control<-trainControl(method = "repeatedcv" ,number = 2, repeats = 2)
model<-train(binary~ .,data= train, method ="ranger" ,trControl= control)
model
```

```{r}
pred<- predict(model,test)
head(pred)
confusionMatrix(pred,test$binary)
```




